### 2019-11-19 NA_paper/manuscript_II/qso_paperII.tex
Before edit NA paper

\documentclass{natureprintstyle}
%\documentclass{nature}
\bibliographystyle{naturemag}
\usepackage{epsfig,caption}
\usepackage{color}
\usepackage{bm}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{amssymb}
\usepackage{rotating}
\usepackage{latexsym}
\usepackage{hyperref}
\usepackage{float}

@@

\newcommand{\ding}[1]{\textcolor{red}{[{\bf Xuheng}: #1]}}

\title{
%From predictions to observation: scaling relations between supermassive black holes and their host galaxies at $1< z<2$
A successful observational test of black hole and galaxy co-evolution models since $z\sim1.7$
%The first comparison between the observation and simulation of the scaling relations between supermassive black holes and their host galaxies at $1.2< z<1.7$
}
\author{Xuheng Ding$^{1,2}$, 
Tommaso Treu$^{1}$, 
John Silverman$^{3, 4}$,
Aklant K. Bhowmick$^{5}$,
N. Menci$^{6}$,
Tiziana Di Matteo$^{5}$,
et. al.
}

@@

\begin{abstract}
Supermassive black holes (SMBHs) ubiquitously occupy the center of massive galaxies in the local Universe and beyond. Their growth in mass (\mbh) appears to be closely linked to the physical properties of their host galaxies\cite{Mag++98, F+M00, M+H03, H+R04, Gul++09}, in particular the relation between \mbh ~and stellar mass. With the origin of this correlation far from being fully understood, simulations have been a promising means to further interpret the observations over the last eight billion years ($z\lesssim1$) thus enabling substantial progress in this field. Constraints at higher redshifts ($z>1$), when most of the SMBHs acquired their mass, are more sensitive to initial conditions and the growth meachanisms and thus may be able to identify inaccurate or missing physics in the models. For this purpose, we have constructed a unique sample of 32 actively-accreting SMBHs at $1.2 < z < 1.7$ ($\sim 8.5-10$ billion years ago) with accurate BH and stellar masses with the latter based on multi-band \hst\ imaging. We directly compare the measurements with two independent state-of-the-art simulations: \texttt{MassiveBlackII} (MBII) and a semi-analytic model (SAM).  After applying the observational selection function to models to account for bias, we find that both \mbii\ and \sam\ agree well with the data, in terms of the central distribution. However, accounting for observational errors, the dispersion in the mass ratio between \mbh~and \mstar~is significantly more consistent with the \mbii\ prediction ($\sim0.3$~dex), than with the \sam\ ($\sim0.7$~dex) one. {\color{red} Hence, our observations can distinguish between the different recipes adopted in the models. The mass relations in \mbii\ are highly dependent on AGN feedback while the relations in the \sam\ are more sensitive to galaxy merger events.} Moreover, the intrinsic scatter in the mass ratio of our high-$z$ sample is comparable to that observed in local sample, all but ruling out the proposed scenario the correlations are purely stochastic in nature arising from some sort of cosmic central limit theorem. Our results support the hypothesis AGN feedback is responsible for a causal link between the SMBH and its host galaxy such that the mass of black holes and that of their host galaxies are tightly correlated.

@@

To understand this connection, recent works~\cite{Park15, Tre++07, Bennert11, Woo++08} have measured the scaling relations out to intermediate redshift {($0.3\lesssim z \lesssim1$)} by studying AGN and their host galaxies with {\it Hubble Space Telescope} ({\it HST}) and found an `observed' evolution in which the growth of SMBHs predates their host galaxies. However, the observational evidence of such evolution at higher-$z$ is under debate since it depends on our understanding of systematic uncertainties and selection effects~\cite{Tre++07,Lauer2007}. Clearly, an improper consideration of the uncertainties and selection effects will lead to an {\it apparent} evolution and result in an overestimate of the evolution\cite{Volonteri2011}.

%Why comparison between data and model.
%Summary of recently works.
%The reason to extend to high redshift.
Simulations are effective at helping to understand this connection and rule out theories/assumptions that could not be definitively verified by observations alone. In particular, simulations can be used to quantify the impact of systematic uncertainties and selection biases with observational data. Recent studies, based on several simulations, show agreement with the observational data at intermediate redshifts ($z\lesssim1$). For example, the state-of-the-art cosmological hydrodynamical simulation of structure formation (\texttt{MassiveBlackII}) has been utilized to compare the predicted scaling relations to \hst\ observation at $0.3<z<1$ that show a positive evolution where the SMBH growth predates that of its the host galaxy~\cite{DeG++15}. Several other works have investigated scaling relations using large-volume simulations, resulting in good agreement with the local relation and some redshift evolution, including the Magneticum Pathfinder SPH Simulations~\cite{Steinborn2015}, the Evolution and Assembly of GaLaxies and their Environments (EAGLE) suite of SPH simulations~\cite{Schaye2015}, and Illustris moving mesh simulation\cite{Sijacki2015, Vogelsberger2014, Li2019}. Besides hydrodynamic simulations, semi-analytic models~\cite{Menci2014, Menci2016} have also made remarkable progress and recovered the local scaling relations~\cite{Kormendy13}. However, comparisons between simulations and the observed scaling relations, based on high-resolution \hst\ imaging, are still mostly limited to $z<1$ due to prior limitations of observational data.

@@

We measure reliable \mbh\ and host properties (i.e., \mstar) with a quantitative assessment of systematic effects. Specifically, \mbh\ is determined using published near-infrared spectroscopic observations of the broad \halpha\ emission line, which eliminates potential systematic uncertainties that may arise from switching to Balmer lines in the local universe to the \Mgii\ or \Civ UV lines for distant galaxies. Regarding the detection of the host galaxies, the X-ray selected nature of the sample results in slightly lower nuclear-to-host ratios, which facilitates the inference of the host light. We employ \hst/WFC3 to obtain high-resolution (0\farcs0642 per pixel) imaging data and adopt a state-of-the-art technique to perform a 2-D flux profile decomposition to measure the light of the host galaxy. Moreover, 21/23 systems have \hst/ACS imaging data, which enable us to assess the colors of the host, hence the rest frame R-band magnitude (\mr) and stellar mass (\mstar) (see Methods and the descriptions in D19). 
%We furthermore combining them with the ground-based photometry to carry out the SED fitting, and thus derive the reliable host rest-frame R band luminosity and stellar mass.

@@

To compare with simulations, we use two independent efforts, \texttt{MassiveBlackII} (MBII)~\cite{Khandai2015} and a semi-analytic model (SAM)~\cite{Menci2014}. These simulations are based on independent model strategies, i.e., hydrodynamic simulation for \mbii\ and semi-analytic model for \sam, respectively. The \mbii\ simulation is the highest resolution at the size of a comoving volume $V_{\rm box} = (100~{\rm Mpc}~h^{-1})$, including a self-consistent model for star formation, black hole accretion, and associated feedback. The large simulation volume enables the model galaxies and SMBHs to evolve independently; the large dynamic range in mass and high spatial resolution meet the requirements to investigate their individual galaxies. While high-resolution N-body simulations can study specific galaxy systems, an understanding of the physical mechanisms influencing the scaling relations require an analytical description of such processes to be implemented into existing semi-analytic models including the \sam. In previous works, \mbii~\cite{Huang2018, DeG++15, Khandai2015,Bhowmick2019} and \sam~\cite{Menci2014, Menci2016} have made high successful predictions, and we refer the interested readers to the Method section for more details.

@@

In Figure~\ref{fig:MM_comp} (left panel), we compare the relation \mbh--\mstar~between observations and the \mbii\ simulation. First, it is clear that the simulated and observed samples are in good agreement. To quantify the agreement level, we perform a linear regression to fit the simulated relations and estimate the best-fit inference and 1$-\sigma$ confidence interval. To make a direct comparison, we fix the same slope value and obtain the best-fit intercept value for the observation. We find that the \mbh-\mstar\ relations are in agreement within the relatively large uncertainties. Furthermore, we compare the scatter of the sample by calculating the standard derivation of the residuals of the linear regression. We find that the simulations and the observations have the same amount of scatter $0.25-0.3$~dex.(see METHODS).

@@

\begin{figure*}[t]%[!b]
\begin{tabular}{c c}
\includegraphics[trim = 0mm 0mm 65mm 0mm, clip, width=0.47\linewidth]{MBII_MM.pdf} &
\includegraphics[trim = 0mm 0mm 65mm 0mm, clip, width=0.47\linewidth]{SAM_MM_consider_nois.pdf} \\
\end{tabular}
\caption{(Left) Comparison of the observed (orange dots) and simulated (blue dots) \mbh--\mstar\ relation. The blue line is the best-fit result for the \mbii\ sample, with the colored region indicating the $1-\sigma$ confidence interval. By fixing the slope to match the simulated data, the orange line shows the best-fit result for the observed data set. The grey cells in the background show the full \mbii\ simulated SMBHs. (Right) The equivalent plot is displayed for the \sam\ sample (green color) in the right panel.}
\label{fig:MM_comp}
\end{figure*}

@@

{\bf In terms of their central distribution, the \mbii\ simulation and \sam\ model are both in agreement with the observational data. However, the scatter distinguishes between the two models. The  the scatter in \mbii\ simulation is consistent to the observational one ($\sim0.3$~dex), while \sam\ sample has significantly larger scatter ($\sim0.7$~dex). Thus, the implementation of AGN feedback in \mbii\ passes our stringent observational test. The \sam\ model also consider the AGN feedback. However, in contrast to \mbii, the feeding process for the SMBH accretion is driven by galaxy mergers, and thus may be more stochastic and lead to the larger scatter. More specifically, in the \sam\ model the encounters are assumed to trigger the feedback, and the fraction of gas that feeds the SMBH is related to the parameters of the  encounter. This introduces additional scatter since it depends on the properties of both interacting galaxies (see Method). As a result, the \sam\ cloud extends to the high \mbh\ with low stellar mass, which may not exist. \ding{To Nicola: do you want to include your new 2D model in the paper?} The consistency between \mbii\ and observations provides important observational evidence in support of the hypothesis that there is a causal link (i.e., AGN feedback) between the evolution of SMBH and that of their host galaxies.
}

@@

\textbf{Imaging data, decomposition and inference of host properties.} 
%1. Imaging data. 2. Inferring host light. 3. Color inference. Rest frame R band and stellar mass.
A detailed description of the \hst\ data analysis can be found in a companion paper (D19). Here we only present a brief summary of that study. We adopted the \hst/WFC3 infrared channel and selected to use the filters F125W $(1.2<z<1.44)$ and F140W $(1.44<z<1.7)$ (according to the redshift of the targets) to observe the imaging data for the 32 AGN systems through the \hst\ program GO-15115 (PI: John Silverman). We obtain six dither exposures with total exposure time $\sim2394s$ and using  {\sc astrodrizzle} software package to co-add the final image with pixel scale as 0\farcs0642. To mitigate the contamination by the background light from both the sky and the detector, we adopt the {\sc photuils} tools to estimate and remove them accurately.

@@

21/32 images in the COSMOS survey also have imaging data in the ACS/F814W with drizzled pixel scale as 0\farcs03, providing us the multi-band information. We decompose the AGN image in the ACS band to obtain the host flux and compare to the WFC3's result to infer the host color. {\bf We find that the $1$~Gyr and $0.625$~Gyr stellar templates could well match the sample color at $z<1.44$ and $z>1.44$ respectively, see Figure~5 in D19, from which we estimate the rest-frame R band luminosity and stellar mass.} A Salpeter initial mass function is employed consistently to the observed and simulated sample.

@@

\textbf{The \texttt{MassiveBlackII} (\mbii) simulation}.  
\mbii\ is a high-resolution cosmological hydrodynamic simulation which ran from $z~=~159$ to $z~=~0.06$ using the Smooth Particle Hydrodynamics~(SPH) code \texttt{P-GADGET}, which is an upgraded version of~\texttt{GADGET-2}~\cite{2005MNRAS.364.1105S}. It has a box size of $100~\mathrm{cMpc/h}$ and $2\times1792^3$ particles. The resolution elements for dark matter and gas have masses of $1.1\times 10^7~M_{\odot}/h$ and $2.2\times 10^6~M_{\odot}/h$, respectively. The base cosmology corresponds to the results of WMAP7 \cite{2011ApJS..192...18K}, i.e., $\Omega_0=0.275$, $\Omega_l=0.725$, $\Omega_b=0.046$, $\sigma_8=0.816$, $h = 0.701$, $n_s=0.968$.  The simulation includes a full modeling of gravity + gas hydrodynamics, as well as a wide range of subgrid recipes for the modeling of star formation \cite{2003MNRAS.339..289S}, black hole growth and feedback processes. Haloes were identified using a Friends-of-Friends (FOF) group finder \cite{1985ApJ...292..371D}. Within these haloes, self-bound substructures/subhaloes were identified using \texttt{SUBFIND} \cite{2005MNRAS.364.1105S}. Galaxies are identified to the stellar matter components of the subhaloes.

For the modeling of black hole growth and associated feedback, we adopt the prescription in the reference \cite{2005Natur.433..604D, 2005MNRAS.361..776S}. In particular, seed black holes of mass $5\times 10^{5}~M_{\odot}/h$ are inserted into haloes of mass $\gtrsim 5\times 10^{10}~M_{\odot}/h$~(if they do not already contain a black hole). Once seeded, black hole growth occurs via gas accretion at a rate given by $\dot{M}_{bh}={4\pi G^2 M_{bh}^2 \rho}/{(c_s^2+v_{bh}^2)^{3/2}}$ where $\rho$ and $c_s$ are the density and sound speed of the ISM gas~(cold phase); $v_{bh}$ is the relative velocity between the black hole and the gas in its vicinity. $10\%$~(radiative efficiency) of the accreted gas is released as radiation. The accretion rate is allowed to be mildly super-Eddington, i.e., limited to two times the Eddington accretion rate. A fraction~($5\%$) of the radiated energy couples to the surrounding gas as black hole~(or AGN) feedback \cite{2005Natur.433..604D}. For the modeling of black hole mergers, two black holes are considered to be merged if their separation distance is within the spatial resolution of the simulation~(the SPH smoothing length), and their relative speeds are lower than the local sound speed of the medium.

For the galaxy photometry, the spectral energy distributions~(SEDs) of the host galaxies were first obtained by summing up the contributions from the individual star particles. The stellar SEDs were modelled using the \texttt{PEGASE-2}~\cite{1999astro.ph.12179F} stellar population synthesis code with a Salpeter IMF. The galaxy SEDs are finally convolved with the desired filter function to obtain the broad band photometry~(SDSS $r$ band magnitude).

For more details regarding the \mbii\ simulation, we refer the reader to the reference~\cite{2015MNRAS.450.1349K}.

\textbf{The semi-analytic model (\sam)}. The \sam\ is based on the description in Menci et al. (2016)~\cite{Menci2016}, to which we refer for details; here we recall its key points. 
The merging trees of dark matter haloes are generated through a Monte Carlo procedure adopting the merging rates given by the Extended Press \& Schechter formalism~\cite{Lacey1993} assuming a Cold Dark Matter power spectrum of perturbations. For each dark matter halo included into a larger halo we computed the dynamical friction process, to  determine whether it will survive as a satellite, or sink to the centre to increase the mass of the central dominant galaxy; binary interactions (fly-by and merging) among satellite sub-halos are also described by the model. In each halo, we compute the amount of gas which cools due to atomic processes. The cooled gas  settles into a rotationally supported disc as the descriptions in the reference~\cite{Mo1998}. The gas is converted into stars through three different channels: quiescent star formation, gradually converting the gas into stars over long timescales $\sim 1$~Gyr; starbursts following galaxy interactions, occurring on timescales $\lesssim 100$~Myr, associated to BH feeding; internal disc instabilities triggering loss of angular momentum resulting into gas inflows toward the centre, therefore feeding star formation and BH accretion. The energy released by the Supernovae associated to the total star formation returns a fraction of the disc gas into the hot phase (stellar feedback).

The semi-analytic model includes BH growth from primordial seeds. These are assumed to originate from PopIII stars with a mass $M_{seed}=100\,M_{\odot}$~\cite{Madau2001}, and to be initially present in all galaxy progenitors. We consider two BH feeding modes: accretion triggered by galaxy interactions and internal disc instabilities. These are described in detail in our previous work~\cite{Menci2016}, and briefly recalled below.\newline
1) BH accretion triggered by interactions. The interaction rate $\tau_r^{-1}=n_T\,\Sigma (r_t,v_c,V)\,V_{rel} (V)$ for galaxies with relative velocity $V_{rel}$ and number density $n_T$ in a common DM halo determines the probability for encounters, 
either fly-by or  merging, through the corresponding cross sections $\Sigma$ given in Menci et al. (2014)~\cite{Menci2014}. The fraction of
gas destabilized in each interaction corresponds to the loss $\Delta j$ of orbital angular momentum $j$, and depends on the mass ratio of the merging partners $M'/M$ and on the impact factor $b$. \newline
2) BH accretion induced by disc instabilities. We assume these to arise  in  galaxies with disc mass exceeding~\cite{Efstathiou1982} $M_{crit} =  {v_{max}^2 R_{d}/ G \epsilon}$ with $\epsilon=0.75$, where $v_{max}$ is the maximum circular velocity associated to each halo \cite{Mo1998}. 
Such a criterion strongly suppresses the probability for disc instabilities to occur not only in massive, gas-poor galaxies, but also in 
dwarf galaxies characterized by small values of the gas-to-DM mass ratios.
The instabilities induce loss of angular momentum resulting into strong inflows that we compute following the 
description in Hopkins et al. (2011)~\cite{Hopkins2011}, recast and extended as in Menci et al. (2014)~\cite{Menci2014}.

>>>>

\documentclass{natureprintstyle}
%\documentclass{nature}
\bibliographystyle{naturemag}
\usepackage{epsfig,caption}
\usepackage{color}
\usepackage{bm}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{amssymb}
\usepackage{rotating}
\usepackage{latexsym}
\usepackage{hyperref}
\usepackage{float}
\usepackage{soul}

@@

\newcommand{\ding}[1]{\textcolor{red}{[{\bf Xuheng}: #1]}} 
\newcommand{\aklant}[1]{\textcolor{blue}{[{\bf AKB}: #1]}} 
\title{
%From predictions to observation: scaling relations between supermassive black holes and their host galaxies at $1< z<2$
A successful observational test of black hole and galaxy co-evolution models since $z\sim1.7$
%The first comparison between the observation and simulation of the scaling relations between supermassive black holes and their host galaxies at $1.2< z<1.7$
}
\author{Xuheng Ding$^{1,2}$, 
Tommaso Treu$^{1}$, 
John D. Silverman$^{3, 4}$,
Aklant K. Bhowmick$^{5}$,
N. Menci$^{6}$,
Tiziana Di Matteo$^{5}$,
et. al.
}

@@

\begin{abstract}
Supermassive black holes (SMBHs) ubiquitously occupy the center of massive galaxies in the local Universe and beyond. Their growth in mass (\mbh) appears to be closely linked to the physical properties of their host galaxies\cite{Mag++98, F+M00, M+H03, H+R04, Gul++09}, in particular the relation between \mbh ~and stellar mass. With the origin of this correlation far from being fully understood, simulations have been a promising means to further interpret the observations over the last eight billion years ($z\lesssim1$) thus enabling substantial progress in this field. Constraints at higher redshifts ($z>1$), when most of the SMBHs acquired their mass, are more sensitive to initial conditions and the growth mechanisms and thus may be able to identify inaccurate or missing physics in the models. For this purpose, we have constructed a unique sample of 32 actively-accreting SMBHs at $1.2 < z < 1.7$ ($\sim 8.5-10$ billion years ago) with accurate BH and stellar masses with the latter based on multi-band \hst\ imaging. We directly compare the measurements with two independent state-of-the-art simulations: \texttt{MassiveBlackII} (MBII) \aklant{hydrodynamic simulation} and a semi-analytic model (SAM).  After applying the observational selection function to models to account for bias, we find that both \mbii\ and \sam\ agree well with the data, in terms of the central distribution. However, accounting for observational errors, the dispersion in the mass ratio between \mbh~and \mstar~is significantly more consistent with the \mbii\ prediction ($\sim0.3$~dex), than with the \sam\ ($\sim0.7$~dex) one. {\color{red} Hence, our observations can distinguish between the different recipes adopted in the models. The mass relations in \mbii ~are highly dependent on AGN feedback while the relations in the \sam\ are more sensitive to galaxy merger events.} Moreover, the intrinsic scatter in the mass ratio of our high-$z$ sample is comparable to that observed in local sample, all but ruling out the proposed scenario the correlations are purely stochastic in nature arising from some sort of cosmic central limit theorem. Our results support the hypothesis \aklant{of} AGN feedback \st{is} \aklant{being} responsible for a causal link between the SMBH and its host galaxy \st{such that the mass of black holes and that of their host galaxies are tightly correlated} \aklant{resulting in a tight correlation between their respective masses}.

@@

To understand this connection, recent works~\cite{Park15, Tre++07, Bennert11, Woo++08} have measured the scaling relations out to intermediate redshift {($0.3\lesssim z \lesssim1$)} by studying AGN and their host galaxies with {\it Hubble Space Telescope} ({\it HST}) and found an `observed' evolution in which the growth of SMBHs predates their host galaxies. However, the observational evidence of such evolution at higher-$z$ is under debate since it depends on our understanding of systematic uncertainties and selection effects~\cite{Tre++07,Lauer2007}. \st{Clearly} \aklant{Therefore}, an improper consideration of the uncertainties and selection effects \st{will} may lead to an {\it apparent} evolution and result in an overestimate of the evolution\cite{Volonteri2011}. \aklant{Comment: `Overestimate of the evolution' sounds a bit odd. Consider rewriting this last sentence}

%Why comparison between data and model.
%Summary of recently works.
%The reason to extend to high redshift.
Simulations are effective at helping to understand this connection and rule out theories/ assumptions that could not be definitively verified by observations alone. In particular, simulations can be used to quantify the impact of systematic uncertainties and selection biases with observational data. Recent studies, based on several simulations, show agreement with the observational data at intermediate redshifts ($z\lesssim1$). For example, the state-of-the-art cosmological hydrodynamical simulation of structure formation (\texttt{MassiveBlackII}) has been utilized to compare the predicted scaling relations to \hst\ observation at $0.3<z<1$ that show a positive evolution where the SMBH growth predates that of its the host galaxy~\cite{DeG++15}. Several other works have investigated scaling relations using large-volume simulations, resulting in good agreement with the local relation and some redshift evolution, including the Magneticum Pathfinder SPH Simulations~\cite{Steinborn2015}, the Evolution and Assembly of GaLaxies and their Environments (EAGLE) suite of SPH simulations~\cite{Schaye2015}, and Illustris moving mesh simulation\cite{Sijacki2015, Vogelsberger2014, Li2019}. Besides hydrodynamic simulations, semi-analytic models~\cite{Menci2014, Menci2016} have also made remarkable progress and recovered the local scaling relations~\cite{Kormendy13}. However, comparisons between simulations and the observed scaling relations, based on high-resolution \hst\ imaging, are still mostly limited to $z<1$ due to prior limitations of observational data.

@@

We measure reliable \mbh\ and host properties (i.e., \mstar) with a quantitative assessment of systematic effects. Specifically, \mbh\ is determined using published near-infrared spectroscopic observations of the broad \halpha\ emission line, which eliminates potential systematic uncertainties that may arise from switching to Balmer lines in the local universe to the \Mgii\ or \Civ UV lines for distant galaxies. Regarding the detection of the host galaxies, the X-ray selected nature of the sample results in slightly lower nuclear-to-host ratios, which facilitates the inference of the host light. We employ \hst/WFC3 to obtain high-resolution (0\farcs0642 per pixel) imaging data and adopt a state-of-the-art technique to perform a 2-D flux profile decomposition to measure the light of the host galaxy. Moreover, 21/23 systems have \hst/ACS imaging data, which enable us to assess the colors of the host, hence the rest frame R-band magnitude (\mr) and stellar mass (\mstar) (see METHODS and the descriptions in D19). 
%We furthermore combining them with the ground-based photometry to carry out the SED fitting, and thus derive the reliable host rest-frame R band luminosity and stellar mass.

@@

To compare with simulations, we use two independent efforts, \texttt{MassiveBlackII} (MBII)~\cite{Khandai2015} and a semi-analytic model (SAM)~\cite{Menci2014}. These simulations are based on independent model strategies, i.e., hydrodynamic simulation for \mbii\ and semi-analytic model for \sam, respectively. The \mbii\ simulation is the highest resolution at the size of a comoving volume $V_{\rm box} = (100~{\rm Mpc}~h^{-1})$, including a self-consistent model for star formation, black hole accretion, and associated feedback. The large simulation volume enables the model galaxies and SMBHs to evolve independently; the large dynamic range in mass and high spatial resolution meet the requirements to investigate their individual galaxies. While high-resolution N-body simulations can study specific galaxy systems, an understanding of the physical mechanisms influencing the scaling relations require an analytical description of such processes to be implemented into existing semi-analytic models including the \sam. In previous works, \mbii~\cite{Huang2018, DeG++15, Khandai2015,Bhowmick2019} and \sam~\cite{Menci2014, Menci2016} have made high successful predictions, and we refer the interested readers to the METHODS section for more details.

@@

In Figure~\ref{fig:MM_comp} (left panel), we compare the relation \mbh--\mstar~between observations and the \mbii\ simulation. First, it is clear that the simulated and observed samples are in good agreement. {\bf To quantify the agreement level, we perform a linear regression to fit the simulated relations and estimate the best-fit inference. To make a direct comparison, we fix the same slope value and obtain the best-fit intercept value for the observation. We find that the \mbh-\mstar\ relations are in agreement within the relatively large scatter of the sample.} Furthermore, we compare the scatter by calculating the standard derivation of the residuals of the linear regression. We find that the simulations and the observations have the same amount of scatter $0.25-0.3$~dex (see METHODS).

@@

\begin{figure*}[t]%[!b]
\begin{tabular}{c c}
\includegraphics[trim = 0mm 0mm 65mm 0mm, clip, width=0.47\linewidth]{MBII_MM.pdf} &
\includegraphics[trim = 0mm 0mm 65mm 0mm, clip, width=0.47\linewidth]{SAM_MM_consider_nois.pdf} \\
\end{tabular}
\caption{(Left) Comparison of the observed (orange dots) and simulated (blue dots) \mbh--\mstar\ relation. The blue line is the best-fit result for the \mbii\ sample, with the colored region indicating the {\bf standard derivation of the sample}. By fixing the slope to match the simulated data, the orange line shows the best-fit result for the observed data set. The grey cells in the background show the full \mbii\ simulated SMBHs. (Right) The equivalent plot is displayed for the \sam\ sample (green color) in the right panel.}
\label{fig:MM_comp}
\end{figure*}

@@

In terms of their central distribution, the \mbii\ simulation and \sam\ model are both in agreement with the observational data. However, the scatter distinguishes between the two models. The  the scatter in \mbii\ simulation is consistent to the observational one ($\sim0.3$~dex), while \sam\ sample has significantly larger scatter ($\sim0.7$~dex). Thus, the implementation of AGN feedback in \mbii\ passes our stringent observational test. The \sam\ model also consider the AGN feedback. However, in contrast to \mbii, the feeding process for the SMBH accretion is driven by galaxy mergers, and thus may be more stochastic and lead to the larger scatter. More specifically, in the \sam\ model the encounters are assumed to trigger the feedback, and the fraction of gas that feeds the SMBH is related to the parameters of the  encounter. This introduces additional scatter since it depends on the properties of both interacting galaxies (see METHODS). As a result, the \sam\ cloud extends to the high \mbh\ with low stellar mass, which may not exist. \ding{To Nicola: do you want to include your new 2D model in the paper?} The consistency between \mbii\ and observations provides important observational evidence in support of the hypothesis that there is a causal link (i.e., AGN feedback) between the evolution of SMBH and that of their host galaxies.

@@

\textbf{HST Observations.} 
%1. Imaging data. 2. Inferring host light. 3. Color inference. Rest frame R band and stellar mass.
A detailed description of the \hst\ data analysis can be found in a companion paper (D19). Here we only present a brief summary of that study. We adopted the \hst/WFC3 infrared channel and selected to use the filters F125W $(1.2<z<1.44)$ and F140W $(1.44<z<1.7)$ (according to the redshift of the targets) to observe the imaging data for the 32 AGN systems through the \hst\ program GO-15115 (PI: John Silverman). We obtain six dither exposures with total exposure time $\sim2394s$ and using  {\sc astrodrizzle} software package to co-add the final image with pixel scale as 0\farcs0642. To mitigate the contamination by the background light from both the sky and the detector, we adopt the {\sc photuils} tools to estimate and remove them accurately.

@@

The COSMOS survey provides \hst\ ACS/F814W imaging data for 21 of 32 AGN in our sample with a drizzled pixel scale as 0\farcs03. We decompose the AGN image in the ACS band to obtain the host flux and compare to the WFC3's result to infer the host color. We find that the $1$~Gyr and $0.625$~Gyr stellar templates could well match the sample color at $z<1.44$ and $z>1.44$ respectively, see Figure~5 in D19, from which we estimate the rest-frame R band luminosity and stellar mass. A Salpeter initial mass function is employed consistently to the observed and simulated sample.

@@

\textbf{\texttt{MassiveBlackII} (\mbii) simulation}.  
\mbii\ is a high-resolution cosmological hydrodynamic simulation using the Smooth Particle Hydrodynamics~(SPH) code \texttt{P-GADGET}, which is an upgraded version of~\texttt{GADGET-2}~\cite{2005MNRAS.364.1105S}. It has a box size of $100~\mathrm{cMpc/h}$ and $2\times1792^3$ particles. The resolution elements for dark matter and gas have masses of $1.1\times 10^7~M_{\odot}/h$ and $2.2\times 10^6~M_{\odot}/h$, respectively. The base cosmology corresponds to the results of WMAP7 \cite{2011ApJS..192...18K}, i.e., $\Omega_0=0.275$, $\Omega_l=0.725$, $\Omega_b=0.046$, $\sigma_8=0.816$, $h = 0.701$, $n_s=0.968$.  The simulation includes a full modeling of gravity + gas hydrodynamics, as well as a wide range of subgrid recipes for the modeling of star formation \cite{2003MNRAS.339..289S}, black hole growth and feedback processes. Haloes were identified using a Friends-of-Friends (FOF) group finder \cite{1985ApJ...292..371D}. Within these haloes, self-bound substructures/subhaloes were identified using \texttt{SUBFIND} \cite{2005MNRAS.364.1105S}. Galaxies are identified to the stellar matter components of the subhaloes.

For the modeling of black hole growth, a feedback prescription is adopted as detailed in the literature \cite{2005Natur.433..604D, 2005MNRAS.361..776S}. In particular, seed black holes of mass $5\times 10^{5}~M_{\odot}/h$ are inserted into haloes of mass $\gtrsim 5\times 10^{10}~M_{\odot}/h$~(if they do not already contain a black hole). Once seeded, black hole growth occurs via gas accretion at a rate given by $\dot{M}_{bh}={4\pi G^2 M_{bh}^2 \rho}/{(c_s^2+v_{bh}^2)^{3/2}}$ where $\rho$ and $c_s$ are the density and sound speed of the ISM gas~(cold phase); $v_{bh}$ is the relative velocity between the black hole and the gas in its vicinity. $10\%$~(radiative efficiency) of the accreted gas is released as radiation. The accretion rate is allowed to be mildly super-Eddington, i.e., limited to two times the Eddington accretion rate. A fraction~($5\%$) of the radiated energy couples to the surrounding gas as black hole~(or AGN) feedback \cite{2005Natur.433..604D}. For the modeling of black hole mergers, two black holes are considered to be merged if their separation distance is within the spatial resolution of the simulation~(the SPH smoothing length), and their relative speeds are lower than the local sound speed of the medium.

For the galaxy photometry, the spectral energy distributions~(SEDs) of the host galaxies were first obtained by summing up the contributions from the individual star particles. The stellar SEDs were modelled using the \texttt{PEGASE-2}~\cite{1999astro.ph.12179F} stellar population synthesis code with a Salpeter IMF. The galaxy SEDs are finally convolved with the desired filter function to obtain the broad band photometry~(SDSS $r$ band magnitude). For further details regarding the \mbii\ simulation, we refer the reader to the reference~\cite{2015MNRAS.450.1349K}.

\textbf{Semi-analytic model (\sam)}. The \sam\ is fully described in Menci et al. (2016)~\cite{Menci2016}. Here, we highlight the main points with respect to our study. The merger trees of dark matter haloes are generated through a Monte Carlo procedure by adopting merger rates using an Extended Press \& Schechter formalism~\cite{Lacey1993} assuming a Cold Dark Matter power spectrum of perturbations. For dark matter halos  that merge with a larger halo, we assess the impact of dynamical friction to determine whether it will survive as a satellite, or sink to the centre to increase the mass of the central dominant galaxy; binary interactions (fly-by and merging), among satellite sub-halos, are also described by the model. In each halo, we compute the amount of gas which cools due through atomic processes and settles into a rotationally-supported disk~\cite{Mo1998}. The gas is converted into stars through three different channels: (1) quiescent star formation gradually converting the gas into stars over long timescales $\sim 1$~Gyr, (2) starbursts following galaxy interactions, occurring on timescales $\lesssim 100$~Myr, associated to BH feeding, (3) internal disc instabilities triggering loss of angular momentum resulting into gas inflows toward the centre thus feeding star formation and BH accretion. The energy released by the supernovae associated with the total star formation returns a fraction of the disc gas into a hot phase (stellar feedback).

The semi-analytic model includes BH growth from primordial seeds. These are assumed to originate from PopIII stars with a mass $M_{seed}=100\,M_{\odot}$~\cite{Madau2001}, and to be initially present in all galaxy progenitors. We consider two BH feeding modes: accretion triggered by galaxy interactions and internal disc instabilities. These are described in detail in our previous work~\cite{Menci2016}, and briefly described below.\newline
1) BH accretion triggered by interactions. The interaction rate $\tau_r^{-1}=n_T\,\Sigma (r_t,v_c,V)\,V_{rel} (V)$ for galaxies with relative velocity $V_{rel}$ and number density $n_T$ in a common DM halo determines the probability for encounters, 
either fly-by or  merging, through the corresponding cross sections $\Sigma$ given in Menci et al. (2014)~\cite{Menci2014}. The fraction of
gas destabilized in each interaction corresponds to the loss $\Delta j$ of orbital angular momentum $j$, and depends on the mass ratio of the merging partners $M'/M$ and on the impact factor $b$. \newline
2) BH accretion induced by disc instabilities. We assume these to arise  in  galaxies with disc mass exceeding~\cite{Efstathiou1982} $M_{crit} =  {v_{max}^2 R_{d}/ G \epsilon}$ with $\epsilon=0.75$, where $v_{max}$ is the maximum circular velocity associated to each halo \cite{Mo1998}. 
Such a criterion strongly suppresses the probability for disc instabilities to occur not only in massive, gas-poor galaxies, but also in 
dwarf galaxies characterized by small values of the gas-to-DM mass ratios.
The instabilities induce loss of angular momentum resulting into strong inflows that we compute following the 
description in Hopkins et al. (2011)~\cite{Hopkins2011}, recast and extended as in Menci et al. (2014)~\cite{Menci2014}.
